\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-17 trunk/setobook.tex
moved concepts section after europa section
updates
europ+concepts touch ups with Javier, fig for arch and updates to arch

% \documentclass[12pt]{svmono}

@@

% \usepackage[agsm]{harvard}

\titlerunning{Towards Deliberative Control of Autonomous Robots}
\authorrunning{K.Rajan et. al.}

\title*{\textbf{\sc Towards Deliberative Control of Autonomous Robots}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \texttt{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \texttt{javier.barreiro@nasa.gov}}

@@

Authors Rajan and Py are funded by a block grant from the David and
Lucile Packard Foundation to MBARI.

>>>>

@@

% \titlerunning{Towards Deliberative Control of Autonomous Robots}
% \authorrunning{K.Rajan et. al.}

\title*{\textbf{\sc Towards Deliberative Control of Autonomous Robots}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

Authors Rajan and Py are funded by a block grant from the David and
Lucile Packard Foundation to MBARI. Rajan and Py would like to thank
their collaborators at MBARI, J. Ryan, J. Harvey, R. Vrijenhoek,
J. Bellingham. They also thank colleagues at NASA Ames who made \eu
available as open source; specifically M. del Alto, D. Korsmeyer and
S. Zornetzer. We are indebted to N. Muscettola for his ideas and early
work at NASA Ames which forms the basis of this work.
